Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2021-01-30 eg6-letters/long-paper/prc-dvcshelium.tex
Add comments from Dan and Sebastian to long P

\documentclass{article}
\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
\usepackage{lineno}
%\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
%\usepackage{amsmath,amssymb}             % AMS Math
%\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern,textcomp}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{epigraph}
\usepackage{natbib}
%\usepackage[scaled]{helvet}
%\usepackage[pagebackref,hyperindex=true]{hyperref}
%\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{array}
\usepackage{amsmath} 
\usepackage{multirow}

@@

\renewenvironment{equation}
  {\linenomathNonumbers\oldequation}
  {\oldendequation\endlinenomath}

@@

\date{\today}
%TODO
\maketitle
\linenumbers

\begin{abstract}
We report on the measurement of the beam-spin asymmetry in the deeply virtual Compton 
scattering off $^4$He using the CEBAF Large Acceptance Spectrometer (CLAS) at
Jefferson Lab using a 6 GeV longitudinally polarized electron beam incident on a 
pressurized $^4$He gaseous target. We detail the method used to ensure the exclusivity 
of the measured reactions, in particular the upgrade of CLAS with a radial time 
projection chamber to detect the 
low-energy recoiling $^4$He nuclei and an inner calorimeter to extend the 
photon detection acceptance at forward angles. Our results confirm the 
theoretically predicted enhancement of the coherent 
($e^4$He~$\to~e'$$^4$He$'\gamma'$) beam-spin asymmetries compared to those 
observed on the free proton, while the incoherent 
($e^4$He~$\to~e'$p$'\gamma'$X$'$) asymmetries exhibit a 30$\%$ suppression.  
From the coherent data, we were able to extract, in a model-independent way, 
the real and imaginary parts of the only $^4$He Compton form factor, $\cal 
H_A$, leading the way toward 3D imaging of the partonic structure of nuclei.
\end{abstract}

@@

In the past few decades, the study of the proton structure has made significant progress
thanks to the theoretical and experimental developments with three dimensional 
structure functions \cite{Anselmino:2015uka}. These studies, which have focused on generalized
parton distributions (GPD) and transverse momentum dependent parton distribution functions (TMD)
can be generalized to the nucleus and offer a unique opportunity to revisit the quark structure 
of the nucleus with an original perspective~\cite{Dupre:2015jha}. This new approach is 
particularly needed as the quark structure of the nucleus remains today the subject of numerous
controversies. Indeed, while much progress has been made in measuring the nuclear
parton distribution functions, their shape remains fundamentally 
unexplained \cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.

In nuclei, the GPDs can be probed conveniently through the measurement of the
spin asymmetries generated by the deeply virtual Compton scattering (DVCS) 
process~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}. The measurement of the exclusive
production of a photon limits the possibilities of final state interactions in the nuclear 
medium and offers a unique opportunity to make a measurement free of final state interactions 
(FSI). Moreover, with a spin-0 nuclear target, the extraction of the GPD from the DVCS data 
is significantly simplified since a single GPD is occurring in the process at leading order. However, the 
measurement of the nuclear DVCS is challenging experimentally and the first attempts by 
the HERMES collaboration \cite{Airapetian:2009cga} led to controversial conclusions. We present here
in detail the more recent measurements by the CLAS collaboration, which has been already partially presented
in two short letters \cite{Hattawy:2017woc,Hattawy:2018liu}. We extend in this article 
the description of the CLAS nuclear DVCS experiment, detail the methods used for the
data analysis and produce the complete experimental results for each channel measured.

@@

The theory of GPDs has been already reviewed in details in various 
publications~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya},
we summarized here only necessary elements to discuss the present experimental results.
The GPDs are real structure functions $F^{q}(x,\xi,t)$, where $x+\xi$ and $x-\xi$ are incoming and outgoing quark momenta 
respectively and $t=\Delta^2$ the squared transferred momentum to the target in this exchange of quarks as illustrated in 
Fig. \ref{fig:GPD}.

@@

The different possible spin states lead to several independent GPDs for any 
given hadron. The proper accounting of the number of GPDs must be done with 
regard to the symmetries of the system. At leading order and leading twist, we 
find that there are $2(2J+1)^2$ GPDs for a particle of spin $J$, 
$i.e.$ for a spin-0 hadron, like the helium-4 nucleus, we will have two GPDs, 
for a spin-1/2 hadron, like the proton, eight GPDs. Half of these involve a 
parton helicity flip, they are called transversity GPDs and do not intervene 
in the DVCS process.

DVCS is the main experimental probe of the GPDs. However, this process does not allow
for an extraction of the GPDs in the full phase space of parameters. Instead, DVCS gives access
to the GPDs integrated over $x$. 
To account for this and simplify equations, we define the complex Compton form factors (CFF,
noted with curved $\mathcal{F}$ for a given GPD $F$) for each GPD as follows:
\begin{equation}
\Re e (\mathcal{F}(\xi,t)) = \sum _q e^2_q \mathcal{P} \int^1_{-1} dx F^{q}(x,\xi,t)
    \left [ {1 \over x - \xi} \mp {1 \over x + \xi} \right], 
\end{equation}
\begin{equation}
\Im m (\mathcal{F}(\xi,t)) = - \pi \sum _q e^2_q \left [ F^{q}(\xi,\xi,t) \mp F^{q}(-\xi,\xi,t) \right]. 
\end{equation} 
These are the quantities directly present in the DVCS cross sections. We note that they are summed over
the different quark flavors present in the hadron, as the electromagnetic probe does not differentiate
quark flavors.

Experimentally, another process is indistinguishable from DVCS, the Bethe-Heitler (BH) 
process in which 
the final state photon is emitted by the scattering lepton rather than the hadron. In this case, the 
photon-hadron interaction is the same as in elastic scattering and depends on the
target form factors rather than its GPDs. The DVCS and BH processes are experimentally 
indistinguishable as they
have identical final states, such that they interfere in the squared amplitude of the
exclusive photo-production process:
\begin{equation}
|T|^2 = |T_{DVCS}|^2 + |T_{BH}|^2 + T_{DVCS}^* T_{BH} + T_{DVCS}T_{BH}^*. 
\end{equation}
The interference terms increase significantly the cross section in specific parts of the phase space
and lead to significant beam spin asymmetries (BSA), which are the focus of the measurements presented 
here.

Finally, we need to define the kinematics. We use the 
conventions from Fig. \ref{fig:PhiAngle} for angles and the experimental kinematic variables
used here are defined as: 
$-t = -(p_p-p_p^\prime)^2 = \Delta^2$ and 
$x_B = {Q^2 \over 2 M_N \nu}\sim {2\xi \over 1+\xi}$, with $M_N$ the nucleon mass and $\nu$ the
energy transfer to the target $\nu = {E -E^\prime} $.

@@

\subsection{Coherent nuclear DVCS}

The first reaction measured in the experiment is the coherent electro-production of a photon on helium
$e+^4\!\!He \rightarrow e+\gamma+^4\!\!He$ at large 4-momentum transfer squared ($Q^2$). The 
leading order diagram of the nuclear coherent DVCS is represented in Fig. \ref{fig:CohDiag}.
In the present experiment, we focused on the measurement of the beam-spin asymmetry (BSA) 
noted $A_{LU}$ with 
$L$ for the longitudinally-polarized electron beam and $U$ the unpolarized target and is defined as:  
\begin{equation}
A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
              {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
  \label{eq:BSA}
\end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the differential cross section for a positive 
(negative) beam helicity. At leading order and leading twist, the BSA can be expressed as \cite{Kirchner:2003wt}:        
\begin{eqnarray}
\label{eq:coh_BSA}
A_{LU}& =& \frac{x_A(1+\epsilon^2)^2}{y} \, s_1^{INT} \sin(\phi) \, 
\bigg/ \, \bigg[ \, \sum_{n=0}^{n=2}c_n^{BH}\cos{(n\phi)} +  \\
& & \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2} P_1(\phi) P_2(\phi) \, c_0^{DVCS} + 
\frac{x_A (1+\epsilon^2)^2}{y} \sum_{n=0}^{n=1} c_n^{INT} \cos{(n\phi)} \bigg].  \nonumber 
\end{eqnarray}
where $\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the BH 
propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and 
$s_1^{INT}$ are the Fourier coefficients of the BH, the DVCS and the 
interference amplitudes for a spin-zero target. The explicit 
expressions of these coefficients, which have been derived based on the work of 
Kirchner and Müller \cite{Kirchner:2003wt}, can be found in Appendix \ref{sec:eq}.

\begin{figure}[tbp!]
\center
\includegraphics[width=9cm]{fig3/DVCS_diagram.pdf}
\caption{Diagram representing the coherent nuclear DVCS.}
\label{fig:CohDiag}
\end{figure}

This formula can be expressed in a simplified manner for a spin-0 target as \cite{Belitsky:2008bz}:
\begin{equation}
A_{LU}(\phi) = \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the CFF $\mathcal{H}_{A}$ associated with the GPD $H_A$ of the 
spin-0 nucleus. The 
$\alpha_{i}$ factors are $\phi$-dependent kinematical terms that depend on the 
nuclear form factor $F_A$ and the independent variables $Q^2$, $x$ and $t$.  
These factors have the following simplified expressions:
\begin{eqnarray}
	\label{eq:alpha1}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2},
	\label{eq:alpha4}
\end{eqnarray}
where $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
leptonic tensor \cite{Belitsky:2008bz}, their explicit expression can be found in 
Appendix \ref{sec:eq}, and $x_{A} = \frac{M_{p}\cdot x}{M_{^4\!He}}$.

The Eq. \ref{eq:A_LU-coh} is particularly convenient to perform an extraction of 
the $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ through a fit of the BSA as 
a function of $\phi$. As can be seen in Fig. \ref{fig:alphas}, the form of each 
$\alpha$ coefficient has a characteristic $\phi$ dependence, such that a fit can
easily separate their respective contributions. The only caveat
is the large difference of magnitude between the $\alpha$ factors, which can lead to 
rather different error propagation for the two parts of the CFF.

\begin{figure}[tbp!]
\center
\includegraphics[width=8cm]{fig3/AlphaCoefs.png}
	\caption{Coefficients presented in Eq. \ref{eq:alpha1} to \ref{eq:alpha4}.
	Note the prescaling factors used for $\alpha_0$, $\alpha_2$ and $\alpha_3$.}
\label{fig:alphas}
\end{figure}

An important issue with the use of this theoretical framework is the large mass of the 
helium nucleus. Recent work indicate that the effect of this correction is moderate 
\cite{Braun:2012bg}, however the applicability to such a large mass remains to be
fully explored from the theoretical point of view.

\subsection{Incoherent nuclear DVCS}

The incoherent nuclear DVCS process, is the DVCS off a bound nucleon in a nucleus
as represented in Fig. \ref{fig:InCohDiag} for an helium-4 target. The remnants of 
the nucleus ($X$) contain only the missing three nucleons. 
The theory for incoherent DVCS on the nucleon is largely based on the free proton theory
already reviewed widely in the literature~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. 
Two important differences need to be accounted for however, the different initial state and the addition of 
final state effects. In the initial state, the intrinsic Fermi motion of the nucleons in the nucleus 
lead to an uncertainty on the exact kinematic of the reaction. Moreover, in general the nucleon 
is in an off-shell state that is not exactly identical to its final state. In the final state, 
interactions between the outgoing nucleon from the DVCS reaction and remnants of the nuclear 
target are possible. The latter leading to contamination from other channels, in particular 
charge exchange processes can lead to a large contribution from such background reaction.

@@

Since, DVCS is a 
process selected using tight exclusivity constrains, some of the initial and final-state effects are
automatically mitigated. Selection criterion on missing energy and momentum are performed,
constraining the range of initial Fermi motion and final interactions possible. However, no theoretical
calculation is available to correct for the reminder of these effects yet. Modern calculations exist 
for such effects in DIS \cite{Cosyn:2017ekf} and quasi-elastic scattering \cite{Ethier:2014bua}
and we can expect them to be extended to the DVCS 
process as more data becomes available. Another avenue of progress
on this topic will be the use of experimental techniques like tagging. This process
can help to control both initial and final state effects by detecting the nuclear remnant.
In the tagged process the target breaks in two providing directly the initial state
of the struck nucleon, while measured backward nuclear fragments limit significantly the
impact of final state effects.

\section{Past nuclear DVCS measurements}

The first measurement of nuclear DVCS has been performed by the HERMES 
collaboration~\cite{Airapetian:2009cga}. This experiment covered an array of 
nuclear targets and looked at the $A$ dependence of the
BSA signal. Their main results, reproduced in Fig. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
from large uncertainties, which makes them consistent with the free proton data and prevents us to
reach strong conclusions about possible nuclear effects. Yet, in the coherent DVCS case a rather
strong effect was expected, leading to a conflict between the HERMES results and theoretical
expectations.

\begin{figure}[tbp!]
\center
	\includegraphics[width=10.5cm]{fig3/HERMES_BSA.png}
	\caption{The sinus moment of the BSA as a function of $-t$ measured by HERMES
	for a series of nuclei \cite{Airapetian:2009cga}, gray bands represent the systematic 
        uncertainties.}
\label{fig:HERMES1}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=10cm]{fig3/HERMES_BSA_2.png}
\caption{The sinus moment of the BSA at low and high $-t$ as a function of $A$ measured by HERMES
	\cite{Airapetian:2009cga}. The inner error bars represent the statistical uncertainty, while 
the outer represent the quadratic sum of the statistical and systematic uncertainties.}
\label{fig:HERMES2}
\end{figure}

An issue with the HERMES measurement and how it is obtained from data has been raised in
\cite{Guzey:2003jh} to explain the discrepancy with theoretical expectations.
The main concern is that the DVCS process is not fully detected and the scattered target
is instead reconstructed through a missing mass measurement of the other reaction products. The 
issue with this method is that the detector resolution is not good enough to separate the 
coherent and incoherent channels properly. 
Instead, the results are labeled "coherent enriched" and "incoherent enriched" at low and high 
$-t$, respectively. This label is based on the assumption that the very different behavior of the
cross sections of the two channels in $t$ will lead to a clear differentiation. However, the
results in Fig. \ref{fig:HERMES2} show similar behaviors in both sectors of $t$, which  
challenges this assumption and could explain the tension between theory and experiment.

Altogether, large error bars and the failure to properly separate the coherent and 
incoherent channels have strongly impaired the interpretation of the measurement 
and the conclusions that could be
obtained from it. The CLAS experiment presented here has profited largely from this
result and was designed specifically to solve these two issues of low statistics and exclusivity.

\section{The CLAS nuclear DVCS experimental setup}

The CLAS nuclear DVCS experiment had for main objectives to explore the coherent DVCS on helium-4, to assess if
the predicted BSA increase could be observed, and to extract the helium-4 GPD. In order to
perform this measurement however, several instrumentation challenges needed to be resolved. First, to
measure the scattered electron and the small angle photon of the DVCS, we used CLAS in its 
DVCS setup, $i.e.$ with the addition of a forward angle calorimeter and a 5-T solenoid magnet. Second, a
radial time projection chamber (RTPC) was installed to measure the
helium recoils and thus ensure the exclusivity of the process in the coherent channel. In this section, we 
will review the important elements of this detection setup.

@@

\subsection{The Radial time projection chamber}

>>>>

\documentclass{article}
\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
%\usepackage{lineno}
%\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
%\usepackage{amsmath,amssymb}             % AMS Math
%\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern,textcomp}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{epigraph}
\usepackage{natbib}
%\usepackage[scaled]{helvet}
%\usepackage[pagebackref,hyperindex=true]{hyperref}
%\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{array}
\usepackage{amsmath} 
\usepackage{multirow}

@@

%\renewenvironment{equation}
%  {\linenomathNonumbers\oldequation}
%  {\oldendequation\endlinenomath}

@@

\date{\today}
%TODO
\maketitle

\begin{abstract}
We report on the measurement of the beam spin asymmetry in the deeply virtual Compton 
scattering off $^4$He using the CEBAF Large Acceptance Spectrometer (CLAS) at
Jefferson Lab using a 6 GeV longitudinally polarized electron beam incident on a 
pressurized $^4$He gaseous target. We detail the method used to ensure the exclusivity 
of the measured reactions, in particular the upgrade of CLAS with a radial time 
projection chamber to detect the 
low-energy recoiling $^4$He nuclei and an inner calorimeter to extend the 
photon detection acceptance at forward angles. Our results confirm the 
theoretically predicted enhancement of the coherent 
($e^4$He~$\to~e'$$^4$He$'\gamma'$) beam spin asymmetries compared to those 
observed on the free proton, while the incoherent 
($e^4$He~$\to~e'$p$'\gamma'$X$'$) asymmetries exhibit a 30$\%$ suppression.  
From the coherent data, we were able to extract, in a model-independent way, 
the real and imaginary parts of the only $^4$He Compton form factor, $\cal 
H_A$, leading the way toward 3D imaging of the partonic structure of nuclei.
\end{abstract}

@@

In the past few decades, the study of the proton structure has made significant progress
thanks to the theoretical and experimental developments of three dimensional 
structure functions \cite{Anselmino:2015uka}. These studies, which have focused on generalized
parton distributions (GPDs) and transverse momentum dependent parton distribution functions (TMDs)
can be generalized to the nucleus and offer a unique opportunity to revisit the quark structure 
of the nucleus with an original perspective~\cite{Dupre:2015jha}. This new approach is 
particularly needed as the quark structure of the nucleus remains today the subject of numerous
controversies. Indeed, while much progress has been made in measuring the nuclear
parton distribution functions, their shape can be explained with very different model 
assumptions~\cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.

In nuclei, the GPDs can be probed conveniently through the measurement of the
spin asymmetries generated by the deeply virtual Compton scattering (DVCS) 
process~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}. The measurement of the exclusive
production of a photon limits the possibilities of final state interactions (FSIs) in the nuclear 
medium and offers a unique opportunity to make a measurement free of them. 
Moreover, with a spin-0 nuclear target, the extraction of the GPD from the DVCS data 
is significantly simplified since a single GPD is involved in the process at leading order. However, the 
measurement of the nuclear DVCS is challenging experimentally and the first attempts by 
the HERMES Collaboration \cite{Airapetian:2009cga} led to controversial conclusions. We present here
in detail the more recent measurements by the CLAS Collaboration, which has been already partially presented
in two short letters \cite{Hattawy:2017woc,Hattawy:2018liu}. We extend in this article 
the description of the CLAS nuclear DVCS experiment, detail the methods used for the
data analysis and produce the complete experimental results for each channel measured.

@@

The theory of GPDs has been already reviewed in detail in various 
publications~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya},
and we summarize here only the necessary elements to discuss the present 
experimental results. The GPDs are real structure functions $F^{q}(x,\xi,t)$, 
where $x+\xi$ and $x-\xi$ are the incoming and outgoing quark momenta respectively 
and $t=\Delta^2$ is the squared transferred four momentum to the target, as 
illustrated in Fig.~\ref{fig:GPD}.

@@

The different possible spin states lead to several independent GPDs for any 
given hadron. The proper accounting of the number of GPDs must be done with 
regard to the symmetries of the system. At leading order and leading twist, we 
find that there are $2(2J+1)^2$ GPDs for a particle of spin $J$. 
Therefore for a spin-0 hadron like the helium-4 nucleus, we will have two GPDs, and 
for a spin-1/2 hadron like the proton, eight GPDs. Half of these involve a 
parton helicity flip, they are called transversity GPDs and do not contribute to 
the DVCS process.

DVCS is the main experimental probe of the GPDs. However, this process does not allow
for an extraction of the GPDs in the full phase space of the parameters. Instead, 
DVCS gives access to the GPDs integrated over $x$. 
To account for this and simplify the notation, we define the complex Compton form factors (CFF,
noted with curved $\mathcal{F}$ for a given GPD $F$) for each GPD as follows:
\begin{equation}
\Re e (\mathcal{F}(\xi,t)) = \sum _q e^2_q \mathcal{P} \int^1_{-1} dx F^{q}(x,\xi,t)
    \left [ {1 \over x - \xi} \mp {1 \over x + \xi} \right], 
\end{equation}
\begin{equation}
\Im m (\mathcal{F}(\xi,t)) = - \pi \sum _q e^2_q \left [ F^{q}(\xi,\xi,t) \mp F^{q}(-\xi,\xi,t) \right]. 
\end{equation} 
These are the quantities directly present in the DVCS cross sections. We note that they are summed over
the different quark flavors present in the hadron, as the electromagnetic probe does not differentiate
quark flavors.

Experimentally, another process is indistinguishable from DVCS, the Bethe-Heitler (BH) 
process in which 
the final state photon is emitted by the scattering lepton rather than the hadron. In this case, the 
photon-hadron interaction is the same as in elastic scattering and depends on the
target form factors rather than its GPDs. The DVCS and BH processes are experimentally 
indistinguishable as they
have identical final states, such that they interfere in the squared amplitude of the
exclusive photo-production process:
\begin{equation}
|T|^2 = |T_{DVCS}|^2 + |T_{BH}|^2 + T_{DVCS}^* T_{BH} + T_{DVCS}T_{BH}^*. 
\end{equation}
The interference terms significantly increase the cross section in specific parts of the phase space
and lead to significant beam spin asymmetries (BSAs), which are the focus of the measurements presented 
here.

Finally, we need to define the kinematics. We use the 
conventions from Fig. \ref{fig:PhiAngle} for angles and the experimental kinematic variables
used here are defined as: 
$-t = -(p_p-p_p^\prime)^2 = \Delta^2$ and 
$x_B = {Q^2 \over 2 M_N \nu}\sim {2\xi \over 1+\xi}$, with $M_N$ the nucleon mass and $\nu$ the
energy transfer to the target, $\nu = {E -E^\prime} $.

@@

\subsection{Coherent Nuclear DVCS}

The first reaction measured in the experiment is the coherent electro-production of a photon on helium
$e+^4\!\!He \rightarrow e^\prime+\gamma+^4\!\!He^\prime$ at large 4-momentum transfer squared ($Q^2$). The 
leading order diagram of the nuclear coherent DVCS is represented in Fig. \ref{fig:CohDiag}.
In the present experiment, we focused on the measurement of the BSA 
noted $A_{LU}$ with 
$L$ for the longitudinally polarized electron beam and $U$ the unpolarized target, which is defined as:  
\begin{equation}
A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
              {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
  \label{eq:BSA}
\end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the differential cross section for a positive 
(negative) beam helicity. At leading order and leading twist, the BSA can be expressed as \cite{Kirchner:2003wt}:        
\begin{eqnarray}
\label{eq:coh_BSA}
A_{LU}& =& \frac{x_A(1+\epsilon^2)^2}{y} \, s_1^{INT} \sin(\phi) \, 
\bigg/ \, \bigg[ \, \sum_{n=0}^{n=2}c_n^{BH}\cos{(n\phi)} +  \\
& & \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2} P_1(\phi) P_2(\phi) \, c_0^{DVCS} + 
\frac{x_A (1+\epsilon^2)^2}{y} \sum_{n=0}^{n=1} c_n^{INT} \cos{(n\phi)} \bigg],  \nonumber 
\end{eqnarray}
where $\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the BH propagators, 
and $x_{A} = \frac{M_{p}\cdot x}{M_{^4\!He}}$. The factors: $c_{0,1,2}^{BH}$, 
$c_0^{DVCS}$, $c_{0,1}^{INT}$ and 
$s_1^{INT}$ are the Fourier coefficients of the BH, the DVCS and the 
interference amplitudes for a spin-zero target, respectively. The explicit 
expressions of these coefficients, which have been derived based on the work of 
Kirchner and Müller \cite{Kirchner:2003wt}, can be found in Appendix \ref{sec:eq}.

\begin{figure}[tbp!]
\center
\includegraphics[width=9cm]{fig3/DVCS_diagram.pdf}
\caption{Diagram representing the coherent nuclear DVCS, where we 
indicate the limit between the hard and the soft components with the dot-dashed factorization line.}
\label{fig:CohDiag}
\end{figure}

This formula can be expressed in a simplified manner for a spin-0 target as \cite{Belitsky:2008bz}:
\begin{equation}
A_{LU}(\phi) = \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts,respectively, of the CFF $\mathcal{H}_{A}$ associated with 
the GPD $H_A$ of the spin-0 nucleus. The 
$\alpha_{i}$ factors are $\phi$-dependent kinematical terms that depend on the 
nuclear form factor $F_A$ and the independent variables $Q^2$, $x$ and $t$.  
These factors have the following simplified expressions:
\begin{eqnarray}
	\label{eq:alpha1}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) \cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2},
	\label{eq:alpha4}
\end{eqnarray}
where $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics found in the 
leptonic tensor \cite{Belitsky:2008bz}. Their explicit expression are provided in 
Appendix \ref{sec:eq}.

Eq. \ref{eq:A_LU-coh} is particularly convenient to perform an extraction of 
$\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ through a fit of the BSA as 
a function of $\phi$. As can be seen in Fig. \ref{fig:alphas}, the form of each 
$\alpha$ coefficient has a characteristic $\phi$ dependence, such that a fit can
easily separate their respective contributions. The only caveat
is the large difference of magnitude between the $\alpha$ factors, which can lead to 
rather different error propagation for the two parts of the CFF.

\begin{figure}[tbp!]
\center
\includegraphics[width=8cm]{fig3/AlphaCoefs.png}
	\caption{Coefficients presented in Eqs. \ref{eq:alpha1} to \ref{eq:alpha4}.
	Note the prescaling factors used for $\alpha_0$, $\alpha_2$ and $\alpha_3$.}
\label{fig:alphas}
\end{figure}

An important issue with the use of this theoretical framework is the large mass of the 
helium nucleus. Recent work indicates that the effect of this correction is moderate 
\cite{Braun:2012bg}, however the applicability to such a large mass remains to be
fully explored from the theoretical point of view.

\subsection{Incoherent Nuclear DVCS}

The incoherent nuclear DVCS process, is the DVCS off a bound nucleon in a nucleus
as represented in Fig. \ref{fig:InCohDiag} for an helium-4 target. The remnants of 
the nucleus ($X$) contain only the missing three nucleons. 
The theory for incoherent DVCS on the nucleon is largely based on the free proton theory
already reviewed widely in the literature~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. 
Two important differences need to be accounted for however: the different initial state and the addition of 
FSIs. In the initial state, the intrinsic Fermi motion of the nucleons in the nucleus 
leads to an uncertainty on the exact kinematics of the reaction. Moreover, in general, the nucleon 
is in an off-shell state that is not exactly identical to its final state. In the final state, 
interactions between the outgoing nucleon from the DVCS reaction and the remnants of the nuclear 
target are possible. The latter leads to contamination from other channels; in particular, 
charge exchange processes can lead to a large contribution from such background reactions.

@@

Since DVCS is a 
process selected using tight exclusivity constraints, some of the initial and final-state effects are
automatically mitigated. Selection criterion on missing energy and momentum are performed,
constraining the range of initial Fermi motion and FSIs possible. However, no theoretical
calculation is available to correct for the reminder of these effects yet. Modern calculations exist 
for such effects in deep inelastic scattering \cite{Cosyn:2017ekf} and quasi-elastic 
scattering \cite{Ethier:2014bua}, and we can expect them to be extended to the DVCS 
process as more data become available. Another avenue of progress
on this topic will be the use of experimental techniques like tagging. This process
can help to control both initial and final state effects by detecting the nuclear remnant.
In the tagged process the target breaks in two, thus measuring the nuclear remnant provides 
information about the initial state of the struck nucleon, while a backward fragment also 
limits significantly the probability of FSIs.

\section{Past Nuclear DVCS Measurements}

The first measurement of nuclear DVCS was performed by the HERMES 
Collaboration~\cite{Airapetian:2009cga}. This experiment covered an array of 
nuclear targets and looked at the $A$ dependence of the
BSA signal. Their main results, reproduced in Figs. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
from large uncertainties, which makes them consistent with the free proton data and prevents us to
reach strong conclusions about possible nuclear effects. Yet, in the coherent DVCS case a rather
strong effect was expected, leading to a conflict between the HERMES results and theoretical
expectations.

\begin{figure}[tbp!]
\center
	\includegraphics[width=10.5cm]{fig3/HERMES_BSA.png}
	\caption{The $\sin(\phi)$ moment of the BSA as a function of $-t$ measured by HERMES
	for a series of nuclei \cite{Airapetian:2009cga}. The gray bands represent the systematic 
        uncertainties.}
\label{fig:HERMES1}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=10cm]{fig3/HERMES_BSA_2.png}
\caption{The $\sin(\phi)$ moment of the BSA at low and high $-t$ as a function of $A$ measured by HERMES
	\cite{Airapetian:2009cga}. The inner error bars represent the statistical uncertainty, while 
the outer represent the quadratic sum of the statistical and systematic uncertainties.}
\label{fig:HERMES2}
\end{figure}

An issue with the HERMES measurement and how it is obtained from data has been raised in
Ref. \cite{Guzey:2003jh} to explain the discrepancy with theoretical expectations.
The main concern is that the DVCS process is not fully detected and the scattered target
is instead reconstructed through a missing mass measurement of the other reaction products. The 
issue with this method is that the detector resolution is not good enough to separate the 
coherent and incoherent channels properly. 
Instead, the results are labeled "coherent enriched" and "incoherent enriched" at low and high 
$-t$, respectively. This label is based on the assumption that the very different behavior of the
cross sections of the two channels in $t$ will lead to a clear differentiation. However, the
results in Fig. \ref{fig:HERMES2} show similar behaviors in both sectors of $t$, which  
challenges this assumption and could explain the tension between theory and experiment.

Altogether, large error bars and the failure to properly separate the coherent and 
incoherent channels have strongly impaired the interpretation of the measurement 
and the conclusions that can be
obtained from it. The CLAS experiment presented here has profited largely from this
result and was designed specifically to solve these two issues of low statistics and exclusivity.

\section{The CLAS Nuclear DVCS Experimental Setup}

The CLAS nuclear DVCS experiment had as its main objectives to explore coherent DVCS on helium-4, to assess if
the predicted BSA increase could be observed, and to extract the helium-4 GPD. In order to
perform this measurement however, several instrumentation challenges needed to be resolved. First, to
measure the scattered electron and the small angle photon from DVCS, we used CLAS in its 
DVCS setup, $i.e.$ with the addition of a forward angle calorimeter and a 5-T solenoid magnet. Second, a
radial time projection chamber (RTPC) was installed to measure the
helium recoils and thus ensure the exclusivity of the process in the coherent channel. In this section, we 
will review the important elements of this detection setup.

@@

\subsection{The Radial Time Projection Chamber}
